Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-10-12 manuscript/Chapter2-SupInfo.Rmd
update supinfo

>>>>

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(data.table)
library(brms)
library(flextable)
library(officer)

```

need to talk about priors here for the gamms etc

```{r, ft.align = "left"}

tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))

set_caption(
  tab1,
  caption = "LOO table",
  style = "Table Caption"
)

```
